---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(daily)
library(dplyr)
```

# daily


The {daily} package converts "daily files" into various 
calendar formats. The primary use case is preparing a 
calendar to accompany a course built from a file that 
can include, in addition to the information displayed
on the calendar, other notes for the intstructor.

See the package vignette for details about daily file syntax 
and various rendering options.

## Installation

You can install from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rpruim/daily")
```

## Example


```{r example, results = "asis"}
library(daily)
library(dplyr)
calendar_css() %>% cat()
cal <-
  daily2cal(
    path  = system.file("daily.txt", package = "daily")
  ) 
cal %>%
  html_calendar(show = 2:6) %>% cat()
```



```{r, results = "asis"}
daily2html(
  path  = system.file("daily.txt", package = "daily"),
  show = 2:6
) %>%
  cat()
```
