---
title: "Using the calendar package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{calendar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

```{r setup}
library(calendar)
library(dplyr)
```

## Overview

The primary use case consists of three steps

1. Create a daily file (a text file with simple markup)
2. Convert the daily file into a data fram with `daily2cal()`
3. Render the calendar as HTML or ggplot.

## Step 1: Daily files

Calendar information can be culled from a "daily file" with with 
following structure.

* Days are separated by an initial `===`
* `===` may optionally be followed by a date
* `===endofcal` terminates the calendar.  All lines after are ignored
* `<item type>:: <item information>` is rendered as information on
a specific date.  For the HTML version, this is converted into a span
so that the appearance can be altered using CSS.


### Example daily file

Here is an example daily file (rendered below).

```{r, echo = FALSE, comment = NA}
system.file("daily.txt", package = "calendar") %>%
  readLines() %>%
  paste(collapse = "\n") %>%
  cat() 
```

## Step 2: Converting to a data frame

`daily2cal()` converts the daily file into a data frame.
To use your own calendar, replace the `path` argument below with
the path to your daily file.

```{r example}
library(calendar)
library(dplyr)
cal <-
  daily2cal(
    path  = system.file("daily.txt", package = "calendar")
  ) 
glimpse(cal)
```

Each time a bare `===` is encountered, the calendar is advanced to the 
next *default* day (see options below).
If a date is specified, it is used, regardless of which days are default days.

## Step 3: Rendering a calendar

The calendar can be rendered as HTML or as a ggplot.
The `show` argument determines which days are displayed (Sunday = 1, 
Saturday = 7).

```{r html, results = "asis"}
calendar_css() %>% cat()
cal %>% html_calendar(show = 2:6) %>% cat()
```

```{r gg, fig.width = 9, fig.height = 3, warning = FALSE}
cal %>% gg_calendar(show = 2:6, size = 4)
```

## Options

The following options may be specified as arguments to `daily2cal()` or as part of the 
YAML header of the daily file.

* `days`: default days. Can be specified as a numeric vector or as a character string (1 = N = Sunday, 5 = R = Thursday, 7 = S = Saturday, etc.)
* `start`: start date for the calendar ("mm/dd/yyyy" format in YAML, date object as argument)
* `end`: start date for the calendar ("mm/dd/yyyy" format in YAML, date object as argument)

Other elements of the YAML header are ignored currently, but can be used to record
information about your calendar.
